Hydras \& Co.: Formalized mathematics in Coq\\ for inspiration and entertainment

### 2021-12-08 doc/JFLA2022/Slides/Slides.tex
a few more slides

\definecolor{plugincolor}{rgb}{0.0,0.0,0.0}
\definecolor{mathcolor}{rgb}{1.0,0.3,0.0}
\definecolor{coqstylecolor}{rgb}{0.0,0.0,01.0}

@@

% End of Alectryon stuff
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title{Hydras \& Co.: Formalized mathematics in Coq\\
 for inspiration and entertainment
}
\date{JFLA, February 2022}
\author{
Pierre Castéran %\inst{1}
\and
    Jérémy Damour %\inst{2}
\and
Karl Palmskog %\inst{3}
\and Clément Pit-Claudel %\inst{4}
\and Théo Zimmermann %\inst{5}
}

% \institute{
% Univ. Bordeaux, CNRS, Bordeaux INP, LaBRI, UMR 5800, F-33400 Talence, France  %\\
%  % \email{pierre.casteran@labri.fr}
% \and
% Univ. de Paris, F-75013 Paris, France
% \and
% KTH Royal Institute of Technology, Stockholm, Sweden
% \and
% MIT CSAIL, Cambridge, Massachusetts, USA
% \and
% Inria, Univ. de Paris, CNRS, IRIF, UMR 8243, F-75013 Paris, France
% }

\begin{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}
  \maketitle
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}
  \frametitle{Coq-community}
  \begin{block}{Objectives}
    \begin{itemize}
    \item \TODO{}{}
    \item\TODO{}{}
      \item Documentation on libraries
    \end{itemize}
  \end{block}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}
  \frametitle{Yet another book on \coq?}
  \begin{block}{Kinds of books}
    \TODO{}{}
  \end{block}

\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}
  \frametitle{Example-driven books}
  \begin{block}{Tsukuba Coq User's Group}
    Regular languages, lambda-calculus, programming language semantics, \dots

   \includegraphics[height=35mm]{tsukubabooks.jpg}
   %\includegraphics[height=45mm]{leaflet.jpg}
     \end{block}
     \begin{block}{\Hydras}
       Kirby \& Paris'  hydra battles, exponentiation algorithms, \dots?
     \end{block}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}
  \frametitle{What hydras are talking about?}
  \begin{block}{}
    \Hydras presents a consistent set of examples, which allow us to formalize 
    \textcolor{mathcolor}{Discrete math}, discuss
    \textcolor{coqstylecolor}{\coq style, specification and proof patterns}, and use  \textcolor{plugincolor}{a few plug-ins}.
  \end{block}
  \begin{block}{Hydra battles}
    \begin{itemize}
\item  \textcolor{mathcolor}{ordinals},
    \textcolor{mathcolor}{rapidly growing functions},
    \textcolor{mathcolor}{primitive recursive functions}, etc.
    \item \textcolor{coqstylecolor}{dependently typed functions},
      \textcolor{coqstylecolor}{proofs of well-foundedness},
         \textcolor{coqstylecolor}{impossibility proofs},
    \textcolor{coqstylecolor}{uniqueness of identity proofs (UIP)},
      \textcolor{coqstylecolor}{indefinite description (Hilbert's epsilon operator)},
    etc.
  \item
 \textcolor{plugincolor}{equations (Matthieu Sozeau)},
    \textcolor{plugincolor}{ackermann (Russel O'Connor)},
      \textcolor{plugincolor}{gaia (Jos\'e Grimm)}
    \end{itemize}
  \end{block}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]
  \frametitle{Tests with Beamer(1)}
  \begin{footnotesize}
      \inputsnippets{Schutte_Ex42a}   
      \inputsnippets{Schutte_Ex42b, Schutte_Ex42c}   
    \end{footnotesize}
\end{frame}
  \begin{frame}[fragile]
    \frametitle{Tests with Beamer(2)}

>>>>

\definecolor{plugincolor}{rgb}{0.6,0.0,0.6}
\definecolor{mathcolor}{rgb}{1.0,0.3,0.0}
\definecolor{coqstylecolor}{rgb}{0.0,0.0,01.0}

@@

% End of Alectryon stuff
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title{Hydras \& Co.: Formalized mathematics in Coq\\
 for inspiration and entertainment
}
\date{JFLA, February 2022}
\author{
Pierre Castéran \inst{1}
\and
    Jérémy Damour \inst{2}
\and
Karl Palmskog \inst{3}
\and Clément Pit-Claudel \inst{4}
\and Théo Zimmermann \inst{5}
}

\institute{
Univ. Bordeaux, CNRS, Bordeaux INP, LaBRI, UMR 5800, F-33400 Talence, France  %\\
 % \email{pierre.casteran@labri.fr}
\and
Univ. de Paris, F-75013 Paris, France
\and
KTH Royal Institute of Technology, Stockholm, Sweden
\and
MIT CSAIL, Cambridge, Massachusetts, USA
\and
Inria, Univ. de Paris, CNRS, IRIF, UMR 8243, F-75013 Paris, France
}

\begin{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}
  \maketitle
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}
  \frametitle{Coq-community}
  \begin{block}{Objectives}
    \begin{itemize}
    \item \TODO{}{}
    \item\TODO{}{}
      \item Documentation on libraries
    \end{itemize}
  \end{block}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}
  \frametitle{Yet another book on \coq?}
  \begin{block}{Kinds of books}
    \TODO{}{}
  \end{block}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}
  \frametitle{Example-driven books (1)}
  \begin{block}{}
    \begin{itemize}
    \item \TODO{}{Definition}
    \item No need to be complete (there is already a reference manual)
      \item No need to introduce \coq (there are already a lot of initiation books and tutorials)
    \item \coq patterns (formalization and proof) are presented  when they are needed.
    \item Allow to compare several different formalizations of a given notion, and several proofs of the same theorem.
    \item By definition, the authors choose topics they like to teach.
      \item \TODO{}{topics adapted to the potential readers?}
    \end{itemize}
  \end{block}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}
  \frametitle{Example-driven books (2)}
  \begin{block}{Tsukuba Coq User's Group}
    Regular languages, lambda-calculus, programming language semantics, \dots

   \includegraphics[height=35mm]{tsukubabooks.jpg}
   %\includegraphics[height=45mm]{leaflet.jpg}
     \end{block}
     \begin{block}{\Hydras}
       Kirby \& Paris'  hydra battles, exponentiation algorithms, \dots
     \end{block}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}
  \frametitle{What hydras are talking about?}
  \begin{block}{}
    \Hydras presents a consistent set of examples, which allow us to formalize 
    some \textcolor{mathcolor}{discrete math}, discuss
    \textcolor{coqstylecolor}{\coq style, specification and proof patterns}, and use\footnote{and depend on!} \textcolor{plugincolor}{a few plug-ins}.
  \end{block}
  \begin{block}{Hydra battles}
    \begin{itemize}
\item  \textcolor{mathcolor}{ordinals},
    \textcolor{mathcolor}{rapidly growing functions},
    \textcolor{mathcolor}{primitive recursive functions}, etc.
    \item \textcolor{coqstylecolor}{dependently typed functions},
      \textcolor{coqstylecolor}{proofs of well-foundedness},
         \textcolor{coqstylecolor}{impossibility proofs},
    \textcolor{coqstylecolor}{uniqueness of identity proofs (UIP)},
      \textcolor{coqstylecolor}{indefinite description (Hilbert's epsilon operator)},
    etc.
  \item
 \textcolor{plugincolor}{equations (Matthieu Sozeau)},
    \textcolor{plugincolor}{ackermann (Russel O'Connor)},
      \textcolor{plugincolor}{gaia (Jos\'e Grimm)}
    \end{itemize}
  \end{block}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]
  \frametitle{Tests with Alectryon(1)}
  \begin{footnotesize}
      \inputsnippets{Schutte_Ex42a}   
      \inputsnippets{Schutte_Ex42b, Schutte_Ex42c}   
    \end{footnotesize}
  \end{frame}
  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \begin{frame}[fragile]
    \frametitle{Tests with Alectryon(2)}
